Towards Verifying the Bitcoin-S Library

### 2020-07-22 paper-short/main.tex
remove images

\graphicspath{{./images/}}

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{Towards Verifying the Bitcoin-S Library} %TODO Please add

%\titlerunning{Dummy short title} %TODO optional, please use if title is longer than one line

@@

\authorrunning{R. Boss and K. Brünnler and A. Doukmak} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Ramon Boss and Kai Brünnler and Anna Doukmak} %TODO mandatory, please use full first names. OASIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

>>>>

\graphicspath{{./images/}{../images/}}

\bibliographystyle{plainurl}
% the mandatory bibstyle

\title{Towards Verifying the Bitcoin-S Library}

% \titlerunning{Dummy short title}
% optional, please use if title is longer than one line

@@

\authorrunning{R. Boss and K. Brünnler and A. Doukmak}
% mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

\Copyright{Ramon Boss and Kai Brünnler and Anna Doukmak}
% mandatory, please use full first names. OASIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
